Reduced plasticity and opportunity for selection across terrestrial ectotherm populations

### 2023-01-09 ms.rmd
Fig 1 complete

##################################
# Loading packages & Functions
##################################
    pacman::p_load(tidyverse,  metafor, flextable, raster, rasterVis,  patchwork, RColorBrewer, ggtree, ape, phytools, viridis, MCMCglmm, brms, latex2exp, orchaRd, multcomp, ggbeeswarm)

@@

Daniel W.A. Noble^1, Fonti Kar^2, Frank Seebacher^3, Alex Bush^4, & Shinichi Nakagawa^2

@@

Applying new effect sizes that allow us to make use of powerful meta-analytic models we: 1) quantify the degree

ectotherms are capable of physiological plasticity in rates: 1)

@@

  #ggsave(p1.2, filename = "./output/figures/fig1.png", width = 11.5, height = 8)
  #ggsave(p1.2.2, filename = "./output/figures/fig1.1.png")

@@

p2 <- p2 + theme_classic() + theme(axis.title  = element_text(size = 24),
        axis.text = element_text(size = 15))
   p2.2 <- p2 + ylim(c(-0.5,0.10)) + theme(legend.position = 'none')
   #ggsave(p2, filename = "./output/figures/fig2.png", width = 11.5, height = 8)
  #ggsave(p2.2, filename = "./output/figures/fig2.2.png")

  phylo / (p1.2/p2) + plot_annotation(tag_levels = "A", tag_suffix = ")")

@@

```{r figphylogeny, fig.wdith = 10, fig.height=9, fig.cap="Phylogenetic tree"}
 # Map data to tree. Just one variable for now
      d <- ggtree(tree, layout="circular") %<+% tree_data

@@

ggsave(filename = "fig4.pdf", path = "./output/figures/", phylo, device = "pdf", width = 10, height = 9, units = "in") 
```

>>>>

##################################
# Loading packages & Functions
##################################
    pacman::p_load(tidyverse,  metafor, flextable, raster, rasterVis,  patchwork, RColorBrewer, ggtree, ape, phytools, viridis, MCMCglmm, brms, latex2exp, orchaRd, multcomp, ggbeeswarm, magick, ggimage)

@@

Daniel W.A. Noble$^1$, Fonti Kar$^2$, Frank Seebacher$^3$, Alex Bush$^4$, & Shinichi Nakagawa$^2$

@@

Applying new effect sizes that allow us to make use of powerful meta-analytic models we: 1) quantify the degree to which aquatic and terrestrial ectotherms are capable of physiological plasticity; 2) test whether the opportunity for selection on physiological traits changes as temperatures rise and 3) test whether climate variability and predictability explain a populations capacity to respond plastically.

@@

  ggsave(p1.2, filename = "./output/figures/fig1.pdf", width = 11.5, height = 8)
  ggsave(p1.2.2, filename = "./output/figures/fig1.1.pdf")

@@

p2 <- p2 + theme_classic() + theme(axis.title  = element_text(size = 24),
        axis.text = element_text(size = 15))
   p2.2 <- p2 + ylim(c(-0.5,0.10)) + theme(legend.position = 'none')
   ggsave(p2, filename = "./output/figures/fig2.pdf", width = 11.5, height = 8)
  ggsave(p2.2, filename = "./output/figures/fig2.2.pdf")

  #(phylo) / (p1.2 / p2) + plot_annotation(tag_levels = "A", tag_suffix = ")")

  fig1 <- image_read("./output/figures/fig1_final.png")
  fig1
```

@@

```{r fig1a, fig.wdith = 10, fig.height=9, fig.cap="Phylogenetic tree"}
 # Map data to tree. Just one variable for now
      d <- ggtree(tree, layout="circular") %<+% tree_data

@@

ggsave(filename = "fig1a_unedited.pdf", path = "./output/figures/", phylo, device = "pdf", width = 10, height = 9, units = "in") 
```
